Repeated incomplete rank observations

### 2020-04-17 inst/cook_repeated.Rmd
more data

H
```

>>>>

	# 17 April 2020:
    rank_likelihood(c(2,4,3,5)) + # person 1 says 5 is the best, 4 the worst.
    rank_likelihood(c(3,5,4,1)) + # person 2 says 1 is the best, 4 the worst.
    rank_likelihood(c(3,2,4,1)) + # person 3 says 1 is the best, 5 the worst.
    rank_likelihood(c(2,5,4  )) + # person 4 says 1 is the best, 5 the worst.
    rank_likelihood(c(5,3,1  ))   # person 5 says 2 is the best, 4 the worst.

```
